Data Management for LSST Special Programs

### 2024-03-27 sec_proc.tex
update 4.2.1

\item \textbf{Repeated pointing --}
Special Programs that require the \emph{exact same} field pointing and 
rotation for \emph{every exposure} (to sub-arcsecond levels) might run 
into hardware boundaries on pointing and tracking.

@@

\textbf{The meaning of ``can be processed".}
This is ultimately left to the discretion of
Rubin Data Management in Rubin Operations, but is expected to include
all standard and alternative visits in sky regions for which a template image exists.
This might also include some non-standard visits (shorter or longer exposures), 
as long as they can be processed by the Prompt pipeline and an appropriate template image exists.
Visits with very short or very long exposure times (or very bright sky 
backgrounds) might be excluded if they would need specialized algorithms for,
e.g., instrument signature removal, difference-imaging, template-generation 
(Section~\ref{ssec:proc_bounds}).
Alert latency requirements do apply to Special Programs data (Section~\ref{ssec:req_proc}),
and if they cannot be met then Prompt processing is ``not possible".

\textbf{The use of specialized (alternative) template images.}
If a Special Program's primary science goal requires specialized templates and 
Prompt processing, the Data Management System will have the capability to load 
and use an alternative template for some sky regions, based on the image metadata 
(i.e., the labels described in Section~\ref{ssec:sci_labels}). 
However, there would not be enough memory to hold alternative templates 
for the whole sky.

>>>>

\item \textbf{Repeated pointing --}
Special Programs that require the \emph{exact same} field pointing and 
rotation for \emph{every exposure} (to sub-arcsecond levels) might run 
into hardware boundaries on pointing and tracking.
Atmospheric distortions also pose a major limitation on positional
repeatability across the focal plane.

@@

\textbf{The meaning of ``can be processed".}
This is ultimately left to the discretion of
Rubin Data Management in Rubin Operations, but is expected to include
all standard and alternative visits in sky regions for which a template image exists.
This might also include some non-standard visits (shorter or longer exposures), 
as long as they can be processed by the Prompt pipeline and an appropriate template image exists.
Visits with very short or very long exposure times (or very bright sky 
backgrounds) might be excluded if they would need specialized algorithms for,
e.g., instrument signature removal, difference-imaging, template-generation 
(Section~\ref{ssec:proc_bounds}).

If, for example, Prompt processing takes longer on Special Programs data or short exposures demand
additional processing because the image acquisition rate exceeds the nominal $\sim$2 per minute,
the available compute capacity of Prompt processing might be saturated.
This could compromise the latency of alert distribution while Special Programs are being executed,
and could also impact alert distribution for subsequent Main Survey visits.
It is left to the discretion of Rubin Data Management to prioritize alert distribution
for Main Survey visits by potentially limiting Prompt processing for Special Programs in such cases.

\textbf{The use of specialized (alternative) template images.}
If a Special Program's primary science goal requires specialized templates and
Prompt processing, the Data Management System will have the capability to load
and use an alternative template for some sky regions, based on the image metadata
(i.e., the labels described in Section~\ref{ssec:sci_labels}).
Potential processes for the creation and verification of such alternative
templates, the cost-benefit of allocating disk storage space to hold
alternative templates, and decisions about when a science goal requires specialized
templates, are left to the discretion of Rubin Data Management.
